Towards Verifying the Bitcoin-S Library

### 2019-06-20 paper/paper.tex
added initial code and todos

\lstset{
  language=scala,
  basicstyle=\footnotesize\ttfamily,
  breaklines=true,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  numbers=left,
  %frame=single, % Border around box
  numbersep=-7pt,
  numberstyle=\color{gray},
  stringstyle=\color{mauve}
}

@@

@@

Here we can see the extracted code needed for the addition of CurrencyUnits:
\lstinputlisting[language=scala]{../code/currsniporig/src/main/scala/code/initial/Code.scala}

>>>>

\lstset{
  language=scala,
  basicstyle=\footnotesize\ttfamily,
  breaklines=true,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  numbers=left,
  %frame=single, % Border around box
  %numbersep=-7pt,
  numberstyle=\color{gray},
  stringstyle=\color{mauve}
}

@@

\todo{
kai text

extracted 3 classes (they are in code/addition/src/main/scala/addition/original)

changes from original to reduced (new folder):
  - package name

  - removed numbers other than Int64

  - removed extending Factory and NetworkElement abstract class. This includes some hex/byte conversion eg fromHex, hex, bytes, fromBytes, ...
    \href{https://bitcoin-s.org/docs/core/core-intro\#the-basics}{description in section \#the-basics (cannot add link with hashtag)}
    \href{https://github.com/bitcoin-s/bitcoin-s/blob/master/core/src/main/scala/org/bitcoins/core/protocol/NetworkElement.scala}{NetworkElement class}
    \href{https://github.com/bitcoin-s/bitcoin-s/blob/master/core/src/main/scala/org/bitcoins/core/util/Factory.scala}{Factory class}

  - removed Bitcoins class

  - removed subtraction and multiplication, binary operations <<, >>, etc, comparision operator <=, >=, etc but not == and !=

  - removed toBigDecimal

  - removed object CurrencyUnits containing some variables to transform satoshis to btc (not used)

  The code we use for the following sections is in reduced folder.
}

@@

Here we can see the extracted code needed for the addition of CurrencyUnits:
\lstinputlisting[language=scala]{../code/addition/src/main/scala/addition/reduced/number/BasicArithmetic.scala}
\lstinputlisting[language=scala]{../code/addition/src/main/scala/addition/reduced/number/NumberType.scala}
\lstinputlisting[language=scala]{../code/addition/src/main/scala/addition/reduced/currency/CurrencyUnits.scala}
